---
title: "Data analysis of CO2 emissions and class structure"
author: "Michael Lindner"
date: "12/07/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = ".")
```

# Preliminaries: Version control

For exact reproducibility of our results we use the package manager `renv` to keep track of the versions of all packages used.

To reproduce our analysis, install `renv` then use `renv::activate()` to activate the environment specified in the lockfile. You might have to use `renv::hydrate()` to install required packages as well. Afterwards you can run the R code as you would normally do.

Troubleshooting: `renv::restore()`



# Preprocessing: extracting the necessary qualitative data from the various datasets

We begin by loading libraries...

```{r message=FALSE}
library("haven")
library("dplyr")
library("readxl")
library("openxlsx")
library(tidyr)
library(formattable)
library(knitr)
library("survey")
library(viridis)
library(mitools)
library(labelled)
library(htmltools)
library(webshot2)
```

All needed data has been added to the lcf_mi file in other scripts
```{r}
mil <- readRDS("../data/lcf_milper.rds")
```

Additional data for validation
```{r}
rawhh <- read_sav("../data/raw/2018_rawhh_ukanon.sav")
rawper <- read_sav("../data/raw/2018_rawper_ukanon_final.sav")

mil <- lapply(
  mil,
  function(x) 
    rawhh %>% 
    select(case, Computer1, Petrol, SameShop) %>%
    mutate_all(~replace_na(., 0)) %>%
    full_join(x, by="case"))

mil <- lapply(
  mil,
  function(x) rawper %>% 
    select(case, RoyalAmt) %>% 
    group_by(case) %>%
    summarize(RoyalAmtHH = sum(RoyalAmt, na.rm=TRUE)) %>%

    full_join(x, by="case"))

```


## Survey


We don't have PSU and Strata, still we can use the weights for the survey. 
Here we use the original data with missing values in HighEdHH.
```{r}
lcf <- mil$`0`
svy <- svydesign(ids = ~1,  weights = lcf$weighta, data = lcf)
```




## Middle classes

Only people with academic degree (HighEdHH == 1) end up in the new middle class.
[UK has a fairly complicated landscape of "sub bachelor degrees" for different professions.]

Start by getting the (weighted) Median income
```{r}
median_income = svyquantile(~EqIncDOp, svy, c(.5))$EqIncDOp[1]
```

```{r}
assign_reckwitz_class <- function(x, upper_threshold = 2.5) {
  # Since accessing columns by name in mutate is not so easy
  # Assuming x[1] is EqIncDOp and x[2] is HighEdHH
  if (x[1] <= 0.7 * median_income) {
    return("lower")
  }
  if (x[1] >  upper_threshold * median_income) {
    return("upper")
  }
  if (is.na(x[2])) {
    return(NA)
  }
  if (x[2] == 1) {
    return("new middle")
  }
  if (x[2] == 10) {
    return("new middle")
  } # student households
  return("old middle")
}

#change this for sensitivity analysis
upper_threshold = 3

mil <-
  lapply(mil, function(x)
    x %>% rowwise %>% mutate(ReckwitzClass = factor(
      assign_reckwitz_class(c(EqIncDOp, HighEdHH), upper_threshold = upper_threshold),
      levels = c("lower", "old middle", "new middle", "upper")
    )))

```


How many Households are affected by the imputation

```{r}
sum(is.na(mil$`0`$ReckwitzClass)) + sum(
  mil$`0`$ReckwitzClass != mil$`1`$ReckwitzClass |
    mil$`0`$ReckwitzClass != mil$`2`$ReckwitzClass |
    mil$`0`$ReckwitzClass != mil$`3`$ReckwitzClass |
    mil$`0`$ReckwitzClass != mil$`4`$ReckwitzClass |
    mil$`0`$ReckwitzClass != mil$`5`$ReckwitzClass |
    mil$`0`$ReckwitzClass != mil$`6`$ReckwitzClass,
  na.rm = T
)
```



For ease of access to the unimputed data, recreate the svy object
```{r}
lcf <- mil$`0`
svy <- svydesign(ids = ~1,  weights = lcf$weighta, data = lcf)
svyby(~EqIncDOp, ~ReckwitzClass, svy, svymean) 
```


Now create a survey object with all multiple imputations. With `mitools` statistics 
of different subset can be combined. This should be used for all analysis.

```{r}
svymi <- svydesign(ids = ~1,  weights = lcf$weighta, data = imputationList(mil[2:7]))

```

# Validation Statistics
```{r}
meat_share = as.formula("~I(
   (C11211t + C11221t + C11231t + C11241t + C11252t + 
    C11251t + C11253t + C11261t + C11271t) /
   (C11111t + C11121t + C11122t + C11131t + C11141t + 
    C11142t + C11151t + C11211t + C11221t + C11231t + 
    C11241t + C11251t + C11252t + C11253t + C11261t + 
    C11271t + C11311t + C11321t + C11331t + C11341t + 
    C11411t + C11421t + C11431t + C11441t + C11451t + 
    C11461t + C11471t + C11511t + C11521t + C11522t + 
    C11531t + C11541t + C11551t + C11611t + C11621t + 
    C11631t + C11641t + C11651t + C11661t + C11671t + 
    C11681t + C11691t + C11711t + C11721t + C11731t + 
    C11741t + C11751t + C11761t + C11771t + C11781t + 
    C11811t + C11821t + C11831t + C11841t + C11851t + 
    C11861t + C11911t + C11921t + C11931t + C11941t + 
    C12111t + C12121t + C12131t + C12211t + C12221t + 
    C12231t + C12241t)
    )")

years_address = as.formula("~I((A131 / p396p) * (p396p < 80))")

age = as.formula("~I(p396p * (p396p < 80))")
```


```{r}
summary_forms <-
  sapply(c("~I(Gorx == 7)"), "~I(A172==2)", meat_share, years_address,
         as.formula)

H_full <-
  sapply(summary_forms, function(x)
    MIcombine(with(svymi, svyby(
      x, ~ ReckwitzClass, svymean, na.rm=TRUE
    ))))


# H_cts <- H_full[1, c(2)] %>% simplify2array %>% as.data.frame
# H_cts[, 1] <- H_cts[, 1] #* 52
# H_cts <- H_cts %>% round(digits = 2)
# #H_cts[, 1] <- H_cts[, 1] %>% round
# colnames(H_cts) <- c("Average age (< 80)")

H_fct <-
  (H_full[1, c(1,2, 3, 4)] %>% simplify2array %>% as.data.frame)[5:8, ]
H_fct <- (H_fct * 100)  %>% round(digits = 2)
colnames(H_fct) <-
  c("% in London", "% no internet", "% meat of total food", "% lifetime spent at address")
rownames(H_fct) <- rownames(H_cts)

# H_cts_SE <-
#   sapply(H_full[2, c(2)], function(x)
#     sqrt(diag(x))) %>% as.data.frame
# H_cts_SE[, 1] <- H_cts_SE[, 1] #* 52
# H_cts_SE <- H_cts_SE %>% round(digits = 2)
# #H_cts_SE[, 1] <- H_cts_SE[, 1] %>% round
# colnames(H_cts_SE) <- colnames(H_cts)
# H_cts_SE <-
#   data.frame(apply(H_cts_SE, c(1, 2), function(x)
#     paste("±", x, sep = "")))

H_fct_SE <-
  (sapply(H_full[2, c(1, 2, 3, 4)], function(x)
    sqrt(diag(x))) %>% as.data.frame)[5:8, ]
H_fct_SE <- (H_fct_SE * 100) %>% round(digits = 2)
colnames(H_fct_SE) <- colnames(H_fct)
rownames(H_fct_SE) <- rownames(H_cts_SE)
H_fct_SE <-
  data.frame(apply(H_fct_SE, c(1, 2), function(x)
    paste("±", x, sep = "")))

S_form <- altbind(
  data.frame(
    H_fct %>% select(1),
    H_fct %>% select(2),
    H_fct %>% select(3),
    H_fct %>% select(4),
    check.names = FALSE
  ),
  data.frame(
    H_fct_SE %>% select(1),
    H_fct_SE %>% select(2),
    H_fct_SE %>% select(3),
    H_fct_SE %>% select(4),
    check.names = FALSE
  )
)
```


```{r}
FT <- formattable(
  S_form,
  list(
    "% in London" = my_color_bar("violet", 100, function(x) {
      x / 100 * 2
    }),
    "SEM" = smallfont,
    "% no internet" = my_color_bar("tomato", 100, function(x) {
      x / 100 * 2
    }),
    "SEM " = smallfont,
    "% meat of total food" = my_color_bar("orange", 100, function(x) {
      x / 100 * 2
    }),
    "SEM  " = smallfont,
    "% lifetime spent at address" = my_color_bar("lightskyblue", 100, function(x) {
      x / 100 * 2
    }),
    "SEM   " = smallfont
  )
)

FT               
```

```{r}
export_formattable(FT,
                   paste(
                     "../plots/",
                     "validation",
                     "_",
                     "upperclass",
                     upper_threshold,
                     ".png",
                     sep = ""
                   ))

```
### Inconclusive 
```{r}
validation_forms <-
  sapply(c("~I(RoyalAmtHH>0)", "~I(Petrol==4)", "~I(Computer1==9)", "~I(SameShop==1)"),
         as.formula)

idx_cts <- c()
idx_fct <- c(1,2,3,4)

H_full <-
  sapply(validation_forms, function(x)
    MIcombine(with(svymi, svyby(
      x, ~ ReckwitzClass, svymean
    ))))


# H_cts <- H_full[1, c(1)] %>% simplify2array %>% as.data.frame
# H_cts <- H_cts %>% round(digits = 2)
# H_cts[, 1] <- H_cts[, 1] %>% round
# colnames(H_cts) <- c("Royalties")

H_fct <-
  (H_full[1, c(1, 2, 3, 4)] %>% simplify2array %>% as.data.frame)[5:8, ]
H_fct <- (H_fct * 100)  %>% round(digits = 2)
colnames(H_fct) <-
  c("% receives royalties", "% electric cars", "% no computer", "% same shops")
rownames(H_fct) <- rownames(H_cts)

# H_cts_SE <-
#   sapply(H_full[2, c(1)], function(x)
#     sqrt(diag(x))) %>% as.data.frame
# H_cts_SE[, 1] <- H_cts_SE[, 1] * 52
# H_cts_SE <- H_cts_SE %>% round(digits = 2)
# H_cts_SE[, 1] <- H_cts_SE[, 1] %>% round
# colnames(H_cts_SE) <- colnames(H_cts)
# H_cts_SE <-
#   data.frame(apply(H_cts_SE, c(1, 2), function(x)
#     paste("±", x, sep = "")))

H_fct_SE <-
  (sapply(H_full[2, c(1,2, 3, 4)], function(x)
    sqrt(diag(x))) %>% as.data.frame)[5:8, ]
H_fct_SE <- (H_fct_SE * 100) %>% round(digits = 2)
colnames(H_fct_SE) <- colnames(H_fct)
rownames(H_fct_SE) <- rownames(H_cts_SE)
H_fct_SE <-
  data.frame(apply(H_fct_SE, c(1, 2), function(x)
    paste("±", x, sep = "")))

S_form <- altbind(
  data.frame(
    H_fct %>% select(1),
    H_fct %>% select(2),
    H_fct %>% select(3),
    H_fct %>% select(4),
    check.names = FALSE
  ),
  data.frame(
    H_fct_SE %>% select(1),
    H_fct_SE %>% select(2),
    H_fct_SE %>% select(3),
    H_fct_SE %>% select(4),
    check.names = FALSE
  )
)

S_form
```
#### Meat Share



```{r}

meat_codes <-
  sapply(c("1.1.5", "1.1.6", "1.1.7", "1.1.8", "1.1.9", "1.1.10"),
         coicop_to_lcf) %>% unlist %>% as.character

food_codes <- coicop_to_lcf(1)

consumption_codes <-
  list(
    meat_codes,
    food_codes
  )


H_full <-
  sapply(consumption_codes, function(x)
    MIcombine(with(
      svymi, svyby(coicop_to_ghg_formula(x), ~ ReckwitzClass, svymean)
    )))


H <- H_full[1, ] %>% simplify2array %>% as.data.frame
H_SE <-
  sapply(H_full[2, ], function(x)
    sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits = 2)
colnames(S) <-
  c("Meat*",
    "All Food*")


S_SE <- (H_SE * 52 / 1000) %>% round(digits = 2)
colnames(S_SE) <- colnames(S)
S_SE <- apply(S_SE, c(1, 2), function(x)
  paste("±", x, sep = ""))



S_Form <- altbind(S, S_SE)


FT <- formattable(
  S_Form,
  align = c("r", "l", "r", "l", "r", "l", "r", "l"),
  list(
    "Meat*" = my_color_bar("orange", 200),
    "SEM" = smallfont,
    "All Food*" = my_color_bar("lightskyblue", 200),
    "SEM " = smallfont
  )
)

FT
```

Meat / food 

```{r}
meat_share = as.formula("~I(
   (C11211t + C11221t + C11231t + C11241t + C11252t + 
    C11251t + C11253t + C11261t + C11271t) /
   (C11111t + C11121t + C11122t + C11131t + C11141t + 
    C11142t + C11151t + C11211t + C11221t + C11231t + 
    C11241t + C11251t + C11252t + C11253t + C11261t + 
    C11271t + C11311t + C11321t + C11331t + C11341t + 
    C11411t + C11421t + C11431t + C11441t + C11451t + 
    C11461t + C11471t + C11511t + C11521t + C11522t + 
    C11531t + C11541t + C11551t + C11611t + C11621t + 
    C11631t + C11641t + C11651t + C11661t + C11671t + 
    C11681t + C11691t + C11711t + C11721t + C11731t + 
    C11741t + C11751t + C11761t + C11771t + C11781t + 
    C11811t + C11821t + C11831t + C11841t + C11851t + 
    C11861t + C11911t + C11921t + C11931t + C11941t + 
    C12111t + C12121t + C12131t + C12211t + C12221t + 
    C12231t + C12241t)
    )")

H_full <-MIcombine(with(
      svymi, svyby(meat_share, ~ ReckwitzClass, svymean, na.rm=T)
    ))


H_full

```
International / All flights 

```{r}
int_share = as.formula("~I(
   (B488 + C73312t) /
   (B488 + C73312t + B487 + C73311t)
    )")

H_full <-MIcombine(with(
      svymi, svyby(int_share, ~ ReckwitzClass, svymean, na.rm=T)
    ))


H_full

```

 Holiday Share
```{r}
int_share = as.formula("~I(
   (B480 + B482 + B484) /
   (B480 + B481 + B482 + B483 + B484 + B485)
    )")

H_full <-MIcombine(with(
      svymi, svyby(int_share, ~ ReckwitzClass, svymean, na.rm=T)
    ))


H_full
```

```{r}
investments = as.formula("~I(P324p)")

H_full <-MIcombine(with(
      svymi, svyby(investments, ~ ReckwitzClass, svymean, na.rm=T)
    ))


H_full
```

```{r}
money_abroad = as.formula("~I(CK4111 / EqIncDOp)")

H_full <-MIcombine(with(
      svymi, svyby(money_abroad, ~ ReckwitzClass, svymean, na.rm=T)
    ))

H_full
```

```{r}
years_address = as.formula("~I((A131 / p396p) * (p396p < 80))")

H_full <-MIcombine(with(
      svymi, svyby(years_address, ~ ReckwitzClass, svymean, na.rm=T)
    ))


H_full
```

```{r}
H_full <-MIcombine(with(
      svymi, svyby(as.formula("~I(A172==1)"), ~ ReckwitzClass, svymean, na.rm=T)
    ))

H_full

```


# Computing GHG for COICOP categories

First we load the bridging table:
```{r}
bridged <- read.xlsx("../data/bridging_matrix_edited.xlsx") %>% slice(2:n())
B <- bridged %>% filter(USE==TRUE)
rm(bridged)
```

We define functions to conveniently access COICOP (sub-)categories

```{r}
# This function returns all used LCF codes that belong to a specific coicop (sub-) category

coicop_to_lcf <- function(category) {
  if (category %in% B$COICOPCODE)  {
    return(B %>% filter(COICOPCODE == category)
           %>% select(LCFCODE) %>% unlist %>% as.character)
  } else {
    category = paste(category, ".", sep = "")
    return(B %>% filter(startsWith(COICOPCODE, category))
           %>% select(LCFCODE) %>% unlist %>% as.character)
  }
}
coicop_to_xp_formula <- function(category) {
  # Division by number of persons in HH (A049)
  if (length(category) != 1)
  {
    return(as.formula(paste(
      "~I((", paste(category, collapse = " + "), ")/A049)"
    )))
  }
  else{
    return(as.formula(paste(
      "~I((", paste(coicop_to_lcf(category), collapse = " + "), ")/A049)"
    )))
  }
}

coicop_to_ghg_formula <- function(category) {
  # Append "GHG_" to access GHG emissions instead of expenditures
  if (length(category) != 1) {
    cats <- paste("GHG_", category,  sep = "")
  }
  else{
    cats <- paste("GHG_", coicop_to_lcf(category),  sep = "")
  }
  # Division by number of persons in HH (A049)
  return(as.formula(paste(
    "~I((", paste(cats, collapse = " + "), ")/A049)"
  )))
}
```

Now lets compute total CO2 for all 12 COICOP categories
```{r}



CO2_full <-
  sapply(as.character(c(1:12)), function(x)
    MIcombine(with(
      svymi, svyby(coicop_to_ghg_formula(x), ~ ReckwitzClass, svymean)
    )))

CO2 <- CO2_full[1, ] %>% simplify2array
CO2_SE <- sapply(CO2_full[2, ], function(x)
  sqrt(diag(x)))

CO2 <- t(CO2)

CO2 <- rbind(CO2, colSums(CO2))
row.names(CO2)[13] <- "Total"


CO2
```


And plot it
```{r}
png(
  paste(
    "../plots/",
    "coicop_co2_classes_relative",
    "_",
    "upperclass",
    upper_threshold,
    ".png",
    sep = ""
  )
)

image(
  round(t(CO2) / rowSums(t(CO2)) * 200)  ,
  xaxt = "n",
  yaxt = "n",
  ylab = "COICOP categories",
  col = rocket(256, direction = -1)
)
#image(t(CO2/ rowSums(CO2)) ,xaxt="n",yaxt="n",ylab="COICOP categories", col=rocket(256, direction= -1))
axis(
  side = 1,
  at = c(0, 0.33, 0.66, 1.0),
  labels = levels(lcf$ReckwitzClass)
)
axis(
  side = 2,
  at = seq(0, 1, 1 / 12),
  labels = row.names(CO2),
  las = 2
)
grid(nx = 4, ny = 13, col = "black")
dev.off()

```

# Utilities for formattable plotting


This can be used for nicer plots later on.
```{r}
#' altbind(df1, SE_df1)
#'
#' Bind together two dataframes in alternating column order
#' Assumes the first on contains mean values, and the second standard errors
altbind <- function(df1, df2) {
  assertthat::assert_that(ncol(df1) == ncol(df2))
  assertthat::are_equal(rownames(df1), rownames(df2))
  df3 <- data.frame(df1[, 1], df2[, 1])
  cns <- c(colnames(df1)[1], "SEM")
  for (i in 2:ncol(df1)) {
    df3 <- data.frame(df3, df1[, i], df2[, i])
    cns <-
      c(cns, colnames(df1)[i], paste("SEM", paste(rep(" ", i - 1), collapse = ""), sep =
                                       ""))
  }
  colnames(df3) <- cns
  rownames(df3) <- rownames(df1)
  return(df3)
}
```



```{r echo = FALSE}
my_proportion <- function(x) {
  x / max(S) # this is bad, it's using a global variable AAAAAHHHH
}
my_color_bar <-
  function (color = "lightgray",
            fixedWidth = 200,
            probfunc = my_proportion,
            ...)
  {
    formatter(
      "span",
      style = function(x)
        style(
          display = "inline-block",
          direction = "rtl",
          `border-radius` = "4px",
          `padding-right` = "2px",
          `background-color` = csscolor(color),
          width = paste(fixedWidth * probfunc(x), "px", sep = ""),
          ...
        )
    )
  }
```

Saving needs this function and packages

```{r}
#library(htmltools)
#library(webshot2)
# Width by default 75% instead of 100%!!!
export_formattable <-
  function(f,
           file,
           width = "65%",
           height = NULL,
           background = "white",
           delay = 0.2,
           zoom = 2)
  {
    w <- as.htmlwidget(f, width = width, height = height)
    path <- html_print(w, background = background, viewer = NULL)
    url <- paste0("file:///", gsub("\\\\", "/", normalizePath(path)))
    webshot(
      url,
      file = file,
      selector = ".formattable_widget",
      zoom = zoom,
      delay = delay,
      vheight = 900
    )
  }
```

```{r}
smallfont <- formatter("span", style = x ~ ifelse(TRUE, "font-size:10px", NA))

```

# T-Test utitiles

```{r}
# from the lodown package

MIsvyttest <- function(formula, design , ...) {
  # the MIcombine function runs differently than a normal svyglm() call
  m <-
    eval(bquote(mitools::MIcombine(with(
      design , survey::svyglm(formula, family = gaussian())
    ))))
  
  rval <- list(
    statistic = coef(m)[2] / survey::SE(m)[2],
    parameter = m$df[2],
    estimate = coef(m)[2],
    null.value = 0,
    alternative = "two.sided",
    method = "Design-based t-test",
    data.name = deparse(formula)
  )
  
  rval$p.value <- (1 - pf((rval$statistic) ^ 2 , 1 , m$df[2]))
  
  names(rval$statistic) <- "t"
  names(rval$parameter) <- "df"
  names(rval$estimate) <- "difference in mean"
  names(rval$null.value) <- "difference in mean"
  class(rval) <- "htest"
  
  return(rval)
  
}

MIsvyttest(
  I(HighEdHH == 1) ~ ReckwitzClass,
  subset(
    svymi,
    ReckwitzClass == "new middle" | ReckwitzClass == "old middle"
  )
)
```
For the t-test formulae

```{r}
coicop_to_ttest_formula <- function(category) {
  # Append "GHG_" to access GHG emissions instead of expenditures
  if (length(category) != 1) {
    cats <- paste("GHG_", category,  sep = "")
  }
  else{
    cats <- paste("GHG_", coicop_to_lcf(category),  sep = "")
  }
  # Division by number of persons in HH (A049)
  return(as.formula(paste(
    "I((", paste(cats, collapse = " + "), ")/A049)~ReckwitzClass"
  )))
}
```


# Summary Statistics

```{r}
summary_forms <-
  sapply(c("~I(HighEdHH==1)", "~EqIncDOp", "~I(Ten1<=2)", "~I(p396p * (p396p < 80))"),
         as.formula)

H_full <-
  sapply(summary_forms, function(x)
    MIcombine(with(svymi, svyby(
      x, ~ ReckwitzClass, svymean
    ))))


H_cts <- H_full[1, c(2)] %>% simplify2array %>% as.data.frame
H_cts[, 1] <- H_cts[, 1] * 52
H_cts <- H_cts %>% round(digits = 2)
H_cts[, 1] <- H_cts[, 1] %>% round
colnames(H_cts) <- c("Equivalised Income")

H_age <- H_full[1, c(4)] %>% simplify2array %>% as.data.frame
H_age <- H_age %>% round(digits = 1)
colnames(H_age) <- c("Average Age (<80)")


H_fct <-
  (H_full[1, c(1, 3)] %>% simplify2array %>% as.data.frame)[5:8, ]
H_fct <- (H_fct * 100)  %>% round(digits = 2)
colnames(H_fct) <-
  c("% academic degree", "% owning home")
rownames(H_fct) <- rownames(H_cts)

H_cts_SE <-
  sapply(H_full[2, c(2)], function(x)
    sqrt(diag(x))) %>% as.data.frame
H_cts_SE[, 1] <- H_cts_SE[, 1] * 52
H_cts_SE <- H_cts_SE %>% round(digits = 2)
H_cts_SE[, 1] <- H_cts_SE[, 1] %>% round
colnames(H_cts_SE) <- colnames(H_cts)
H_cts_SE <-
  data.frame(apply(H_cts_SE, c(1, 2), function(x)
    paste("±", x, sep = "")))

H_age_SE <-
  sapply(H_full[2, c(4)], function(x)
    sqrt(diag(x))) %>% as.data.frame
H_age_SE <- H_age_SE %>% round(digits = 1)
colnames(H_age_SE) <- colnames(H_age)
H_age_SE <-
  data.frame(apply(H_age_SE, c(1, 2), function(x)
    paste("±", x, sep = "")))

H_fct_SE <-
  (sapply(H_full[2, c(1, 3, 4)], function(x)
    sqrt(diag(x))) %>% as.data.frame)[5:8, ]
H_fct_SE <- (H_fct_SE * 100) %>% round(digits = 2)
colnames(H_fct_SE) <- colnames(H_fct)
rownames(H_fct_SE) <- rownames(H_cts_SE)
H_fct_SE <-
  data.frame(apply(H_fct_SE, c(1, 2), function(x)
    paste("±", x, sep = "")))

S_form <- altbind(
  data.frame(
    H_fct %>% select(1),
    H_cts %>% select(1),
    H_fct %>% select(2),
    H_age %>% select(1),
    check.names = FALSE
  ),
  data.frame(
    H_fct_SE %>% select(1),
    H_cts_SE %>% select(1),
    H_fct_SE %>% select(2),
    H_age_SE %>% select(1),
    check.names = FALSE
  )
)
```


```{r}
FT <- formattable(
  S_form,
  list(
    "% academic degree" = my_color_bar("violet", 100, function(x) {
      x / 100
    }),
    "SEM" = smallfont,
    "Equivalised Income" = my_color_bar("tomato", 100, proportion),
    "SEM " = smallfont,
    "% owning home" = my_color_bar("orange", 100, function(x) {
      x / 100
    }),
    "SEM  " = smallfont,
    "Average Age (<80)" = my_color_bar("lightskyblue", 100, proportion),
    "SEM   " = smallfont
  )
)

FT               
```

```{r}
export_formattable(FT,
                   paste(
                     "../plots/",
                     "summary",
                     "_",
                     "upperclass",
                     upper_threshold,
                     ".png",
                     sep = ""
                   ))

```





## HighEdHH in NMC not due to student households
```{r}

MIcombine(with(svymi, svyby( ~ I(HighEdHH == 1), ~ ReckwitzClass, svymean)))

```

# Totals

```{r}
glm_formula <-
  lcf %>% colnames %>% grep("GHG_", . , value = TRUE) %>% paste(collapse = " + ") %>% paste("I((", . , ")/A049) ~ EqIncDOp + I(HighEdHH==1)", sep = "") %>% formula

lin <- with(svymi, svyglm(glm_formula))

# for (mod in lin) {show(summ(mod))}

```




```{r}
# Households
#pop_per_class <- MIcombine(with(svymi, svytotal(~ReckwitzClass)))
# Persons
pop_per_class <-
  MIcombine(with(svymi, svyby( ~ A049, ~ ReckwitzClass, svytotal)))
H <- pop_per_class$coefficients %>% round
H_SE <- pop_per_class$variance %>% diag %>% sqrt
```


```{r}
total_co2_formula <-
  lcf %>% colnames %>% grep("GHG_", . , value = TRUE) %>% paste(collapse = " + ") %>% paste("~I(", . , ")", sep = "") %>% as.formula
co2_per_class <-
  MIcombine(with(svymi, svyby(
    total_co2_formula, ~ ReckwitzClass, svytotal
  )))
S <- (co2_per_class$coefficients * 52 / 1e6) %>% round
S_SE <-
  ((co2_per_class$variance %>% diag %>% sqrt) * 52 / 1e6) %>% round
```


```{r}

leng = 512
png(
  paste(
    "../plots/",
    "totals_per_class",
    "_",
    "upperclass",
    upper_threshold,
    ".png",
    sep = ""
  ),
  height = leng,
  width = 2 * leng
)

# Create data

dat <- cbind(H, S)
colnames(dat) <- c("Population", "CO2")
rownames(dat) <- c("lower", "old middle", "new middle", "upper")

# create color palette:
library(RColorBrewer)
coul <- brewer.pal(4, "Set2")

# Transform this data in %
data_percentage <- apply(dat, 2, function(x) {
  x * 100 / sum(x)
})

# Enable plotting outside
cfactor = 2.8
par(
  mar = c(3, 6, 3, 20),
  xpd = TRUE,
  cex.lab = cfactor,
  cex.axis = cfactor,
  cex.main = cfactor,
  cex.sub = cfactor,
  pty = "m"
)

# Make a stacked barplot--> it will be in %!
bp <-
  barplot(data_percentage,
          col = coul,
          border = "white",
          ylab = "% of total")
legend(
  "topright",
  legend = rev(rownames(dat)),
  fill = rev(coul),
  inset = c(-.41, 0),
  box.col = "white",
  cex = cfactor
)


y_pop <-
  c(
    data_percentage[1, 1] / 2,
    sum(data_percentage[1:2, 1]) - data_percentage[2, 1] / 2,
    sum(data_percentage[1:3, 1]) - data_percentage[3, 1] / 2,
    sum(data_percentage[, 1])
  )

y_pop <- c(
  data_percentage[1, 1] - 5,
  sum(data_percentage[1:2, 1]) - 5,
  sum(data_percentage[1:3, 1]) - 5,
  sum(data_percentage[, 1]) + 1
)
y_co2 <- c(
  data_percentage[1, 2] - 3,
  sum(data_percentage[1:2, 2]) - 5,
  sum(data_percentage[1:3, 2]) - 5,
  sum(data_percentage[, 2])
)



xpos <- c(.7, .7, .7, .7, 1.9, 1.9, 1.9, 1.9)
ypos <- c(y_pop, y_co2)
text(
  bp,
  x = xpos,
  y = ypos,
  labels = paste(as.vector(round(
    data_percentage, digits = 1
  )), "%")
  ,
  pos = 1,
  cex = cfactor
)

dev.off()
```





# High Level View on CO2

```{r echo = FALSE}





highlevel_codes <- list(
  coicop_to_lcf("4"),
  coicop_to_lcf("7"),
  setdiff(
    B %>% select(LCFCODE) %>% unlist %>% as.character,
    c(coicop_to_lcf("4"), coicop_to_lcf("7"))
  ),
  B %>% select(LCFCODE) %>% unlist %>% as.character
)

H_full <-
  sapply(highlevel_codes, function(x)
    MIcombine(with(
      svymi, svyby(coicop_to_ghg_formula(x), ~ ReckwitzClass, svymean)
    )))

H <- H_full[1, ] %>% simplify2array %>% as.data.frame
H_SE <-
  sapply(H_full[2, ], function(x)
    sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits = 2)
colnames(S) <- c("Housing", "Mobility", "Other", "Total")


S_SE <- (H_SE * 52 / 1000) %>% round(digits = 2)
colnames(S_SE) <- c("Housing", "Mobility", "Other", "Total")
S_SE <- apply(S_SE, c(1, 2), function(x)
  paste("±", x, sep = ""))


S_Form <- altbind(S, S_SE)
```


```{r echo = FALSE}


FT <- formattable(
  S_Form,
  align = c("r", "l", "r", "l", "r", "l"),
  list(
    "Housing" = my_color_bar("orange"),
    "SEM" = smallfont,
    "Mobility" = my_color_bar("lightskyblue"),
    "SEM " = smallfont,
    "Other" = my_color_bar("violet"),
    "SEM  " = smallfont,
    "Total" = my_color_bar("tomato"),
    "SEM   " = smallfont
  )
)
FT
```



```{r}
export_formattable(
  FT,
  paste(
    "../plots/",
    "highlevel",
    "_",
    "upperclass",
    upper_threshold,
    ".png",
    sep = ""
  )
)
```


T-testing of middle class differences

```{r}
T_full <-
  sapply(highlevel_codes, function(x)
    MIsvyttest(
      coicop_to_ttest_formula(x),
      subset(
        svymi,
        ReckwitzClass == "new middle" | ReckwitzClass == "old middle"
      )
    ))
T_full
```




# Zoom in...
##... on Housing

```{r}
housing_codes <- list(
  coicop_to_lcf("4.4.1"),
  coicop_to_lcf("4.4.2"),
  setdiff(coicop_to_lcf("4"), c(
    coicop_to_lcf("4.4.1"), coicop_to_lcf("4.4.2")
  )),
  coicop_to_lcf("4")
)



H_full <-
  sapply(housing_codes, function(x)
    MIcombine(with(
      svymi, svyby(coicop_to_ghg_formula(x), ~ ReckwitzClass, svymean)
    )))
```


```{r}
H <- H_full[1, ] %>% simplify2array %>% as.data.frame
H_SE <-
  sapply(H_full[2, ], function(x)
    sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits = 2)
colnames(S) <- c("Electricity", "Gas", "Other Housing", "Total")


S_SE <- (H_SE * 52 / 1000) %>% round(digits = 2)
colnames(S_SE) <- c("Electricity", "Gas", "Other Housing", "Total")
S_SE <- apply(S_SE, c(1, 2), function(x)
  paste("±", x, sep = ""))


S_Form <-
  altbind(data.frame(S, check.names = FALSE),
          data.frame(S_SE, check.names = FALSE))

FT <- formattable(
  S_Form,
  align = c("r", "l", "r", "l", "r", "l", "r", "l"),
  list(
    "Electricity" = my_color_bar("orange", 100),
    "SEM" = smallfont,
    "Gas" = my_color_bar("lightskyblue", 100),
    "SEM " = smallfont,
    "Other Housing" = my_color_bar("violet", 100),
    "SEM  " = smallfont,
    "Total" = my_color_bar("tomato", 100),
    "SEM   " = smallfont
  )
)


FT

```

```{r}
export_formattable(FT,
                   paste(
                     "../plots/",
                     "housing",
                     "_",
                     "upperclass",
                     upper_threshold,
                     ".png",
                     sep = ""
                   ))
```

T-testing of middle class differences

```{r}
T_full <-
  sapply(housing_codes, function(x)
    MIsvyttest(
      coicop_to_ttest_formula(x),
      subset(
        svymi,
        ReckwitzClass == "new middle" | ReckwitzClass == "old middle"
      )
    ))
T_full
```

## ... on Mobility



```{r}
# car_codes: "7.1." - "7.1.3.3" + "7.2." - "7.2.1.4" + "7.3.4.7" (car leasing)
# other: "7.1.3.3" + "7.2.1.4" (bicycles) + "7.3.4.4" + "7.3.4.5" (taxis and other) + "7.3.4.6" (car, van, bicycle hire)
# public transport: 7.3.1, 7.3.2, 7.3.3, 7.3.4.3(school), 7.3.4.8(water)
# air transport: 7.3.4.1, 7.3.4.2

car_codes <-
  setdiff(sapply(c("7.1", "7.2", "7.3.4.7"), coicop_to_lcf) %>% unlist,
          sapply(c("7.1.3.3", "7.2.1.4"), coicop_to_lcf) %>% unlist)
pubtrans_codes <-
  sapply(c("7.3.1", "7.3.2", "7.3.3", "7.3.4.3", "7.3.4.8"),
         coicop_to_lcf) %>% unlist %>% as.character

air_codes <-
  sapply(c("7.3.4.1", "7.3.4.2"), coicop_to_lcf) %>% unlist %>% as.character

mobility_codes <-
  list(car_codes, pubtrans_codes, air_codes, coicop_to_lcf(7))


H_full <-
  sapply(mobility_codes, function(x)
    MIcombine(with(
      svymi, svyby(coicop_to_ghg_formula(x), ~ ReckwitzClass, svymean)
    )))


H <- H_full[1, ] %>% simplify2array %>% as.data.frame
H_SE <-
  sapply(H_full[2, ], function(x)
    sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits = 2)
colnames(S) <- c("Cars", "Public", "Air", "Total")


S_SE <- (H_SE * 52 / 1000) %>% round(digits = 2)
colnames(S_SE) <- c("Cars", "Public", "Air", "Total")
S_SE <- apply(S_SE, c(1, 2), function(x)
  paste("±", x, sep = ""))



internet_full <-
  MIcombine(with(svymi, svyby(
    coicop_to_ghg_formula("8.4"), ~ ReckwitzClass, svymean
  )))
Internet <-
  (internet_full$coefficients * 52 / 1000) %>% round(digits = 3)
internet_SE <- internet_full$variance  %>% diag %>% sqrt
internet_SE <- (internet_SE *  52 / 1000) %>% round(digits = 4)
internet_SE <- sapply(internet_SE, function(x)
  paste("±", x, sep = ""))

S_Form <-
  altbind(data.frame(S, Internet, check.names = FALSE),
          data.frame(S_SE, internet_SE))


FT <- formattable(
  S_Form,
  align = c("r", "l", "r", "l", "r", "l", "r", "l"),
  list(
    "Cars" = my_color_bar("orange", 100),
    "SEM" = smallfont,
    "Public" = my_color_bar("lightskyblue", 100),
    "SEM " = smallfont,
    "Air" = my_color_bar("violet", 100),
    "SEM  " = smallfont,
    "Total" = my_color_bar("tomato", 100),
    "SEM   " = smallfont,
    "Internet" = my_color_bar("pink", 50, proportion),
    "SEM    " = smallfont
  )
)


FT
```

```{r}
export_formattable(
  FT,
  paste(
    "../plots/",
    "mobility",
    "_",
    "upperclass",
    upper_threshold,
    ".png",
    sep = ""
  )
)

```

T-testing of middle class differences

```{r}
T_full <-
  sapply(mobility_codes, function(x)
    MIsvyttest(
      coicop_to_ttest_formula(x),
      subset(
        svymi,
        ReckwitzClass == "new middle" | ReckwitzClass == "old middle"
      )
    ))
T_full
```

## ... on Other Indirect Consumption



```{r}

all_consumption_codes <-
  setdiff(B %>% select(LCFCODE) %>% unlist %>% as.character,
          c(coicop_to_lcf("4"), coicop_to_lcf("7")))


meat_codes <-
  sapply(c("1.1.5", "1.1.6", "1.1.7", "1.1.8", "1.1.9", "1.1.10"),
         coicop_to_lcf) %>% unlist %>% as.character

other_food_codes <- setdiff(coicop_to_lcf(1), meat_codes)

other_consumption_codes <-
  setdiff(all_consumption_codes,
          c(meat_codes, other_food_codes, coicop_to_lcf(11))) # COICOP 11 -> Restaurants, Holidays

consumption_codes <-
  list(
    meat_codes,
    other_food_codes,
    coicop_to_lcf(11),
    other_consumption_codes,
    all_consumption_codes
  ) #


H_full <-
  sapply(consumption_codes, function(x)
    MIcombine(with(
      svymi, svyby(coicop_to_ghg_formula(x), ~ ReckwitzClass, svymean)
    )))


H <- H_full[1, ] %>% simplify2array %>% as.data.frame
H_SE <-
  sapply(H_full[2, ], function(x)
    sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits = 2)
colnames(S) <-
  c("Meat*",
    "Other Food*",
    "Restaurants, Holidays*",
    "Miscellaneous",
    "Total")# "Other Consumption"


S_SE <- (H_SE * 52 / 1000) %>% round(digits = 2)
colnames(S_SE) <- colnames(S)
S_SE <- apply(S_SE, c(1, 2), function(x)
  paste("±", x, sep = ""))



S_Form <- altbind(S, S_SE)


FT <- formattable(
  S_Form,
  align = c("r", "l", "r", "l", "r", "l", "r", "l"),
  list(
    "Meat*" = my_color_bar("orange", 200),
    "SEM" = smallfont,
    "Other Food*" = my_color_bar("lightskyblue", 200),
    "SEM " = smallfont,
    "Restaurants, Holidays*" = my_color_bar("violet", 200),
    "SEM  " = smallfont,
    "Miscellaneous" = my_color_bar("pink", 100),
    "SEM   " = smallfont,
    "Total" = my_color_bar("tomato", 100),
    "SEM    " = smallfont
  )
)

FT
```

```{r}
export_formattable(
  FT,
  paste(
    "../plots/",
    "consumption",
    "_",
    "upperclass",
    upper_threshold,
    ".png",
    sep = ""
  )
)
```

T-testing of middle class differences

```{r}
T_full <-
  sapply(consumption_codes, function(x)
    MIsvyttest(
      coicop_to_ttest_formula(x),
      subset(
        svymi,
        ReckwitzClass == "new middle" | ReckwitzClass == "old middle"
      )
    ))
T_full
```
