---
title: "Data analysis of CO2 emissions and class structure"
author: "Michael Lindner"
date: "5/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = ".")
```

# Preliminaries: Version control

For exact reproducibility of our results we use the package manager `renv` to keep track of the versions of all packages used.

To reproduce our analysis, install `renv` then use `renv::activate()` to activate the environment specified in the lockfile. You might have to use `renv::hydrate()` to install required packages as well. Afterwards you can run the R code as you would normally do.

Troubleshooting: `renv::restore()`



# Preprocessing: extracting the necessary qualitative data from the various datasets

We begin by loading libraries...

```{r message=FALSE}
library("haven")
library("dplyr")
library("readxl")
library("openxlsx")
library(tidyr)
library(formattable)
library(knitr)
library("survey")
library(viridis)
library(mitools)
library(labelled)
library(htmltools)
library(webshot2)
```

All needed data has been added to the lcf_mi file in other scripts
```{r}
mil <- readRDS("../data/lcf_milper.rds")
```

## Survey


We don't have PSU and Strata, still we can use the weights for the survey. 
Here we use the original data with missing values in HighEdHH.
```{r}
lcf <- mil$`0`
svy <- svydesign(ids = ~1,  weights = lcf$weighta, data = lcf)
```




## Middle classes

Only people with academic degree (HighEdHH == 1) end up in the new middle class.
[UK has a fairly complicated landscape of "sub bachelor degrees" for different professions.]

Start by getting the (weighted) Median income
```{r}
median_income = svyquantile(~EqIncDOp, svy, c(.5))$EqIncDOp[1]
```

```{r}
assign_reckwitz_class <- function(x, upper_threshold = 2.5) {
  # Since accessing columns by name in mutate is not so easy
  # Assuming x[1] is EqIncDOp and x[2] is HighEdHH
  if (x[1] <= 0.7 * median_income) { return("lower") }
  if (x[1] >  upper_threshold * median_income) { return("upper") }
  if (is.na(x[2])) { return(NA) }
  if (x[2] == 1) { return("new middle") }
  if (x[2] == 10) { return("new middle") } # student households
  return("old middle")
}

#change this for sensitivity analysis
upper_threshold = 2

mil <- lapply(mil, function(x) x %>% rowwise %>% mutate(ReckwitzClass = factor(assign_reckwitz_class(c(EqIncDOp,HighEdHH), upper_threshold = upper_threshold), levels = c("lower", "old middle", "new middle", "upper"))))

```


How many Households are affected by the imputation

```{r}
sum(is.na(mil$`0`$ReckwitzClass)) + sum(mil$`0`$ReckwitzClass != mil$`1`$ReckwitzClass |
      mil$`0`$ReckwitzClass != mil$`2`$ReckwitzClass |
      mil$`0`$ReckwitzClass != mil$`3`$ReckwitzClass |
      mil$`0`$ReckwitzClass != mil$`4`$ReckwitzClass |
      mil$`0`$ReckwitzClass != mil$`5`$ReckwitzClass |
      mil$`0`$ReckwitzClass != mil$`6`$ReckwitzClass, na.rm=T)
```



For ease of access to the unimputed data, recreate the svy object
```{r}
lcf <- mil$`0`
svy <- svydesign(ids = ~1,  weights = lcf$weighta, data = lcf)
svyby(~EqIncDOp, ~ReckwitzClass, svy, svymean) 
```


Now create a survey object with all multiple imputations. With `mitools` statistics 
of different subset can be combined. This should be used for all analysis.

```{r}
svymi <- svydesign(ids = ~1,  weights = lcf$weighta, data = imputationList(mil[2:7]))

```


# Computing GHG for COICOP categories

First we load the bridging table:
```{r}
bridged <- read.xlsx("../data/bridging_matrix_edited.xlsx") %>% slice(2:n())
B <- bridged %>% filter(USE==TRUE)
rm(bridged)
```

We define functions to conveniently access COICOP (sub-)categories

```{r}
# This function returns all used LCF codes that belong to a specific coicop (sub-) category

coicop_to_lcf <- function(category) {
  if (category %in% B$COICOPCODE)  {
    return(B %>% filter(COICOPCODE == category) 
         %>% select(LCFCODE) %>% unlist%>% as.character)
  } else {
  category = paste(category,".",sep="") 
  return(B %>% filter(startsWith(COICOPCODE,category)) 
         %>% select(LCFCODE) %>% unlist%>% as.character)
  }
}
coicop_to_xp_formula <- function(category) {
  # Division by number of persons in HH (A049)
if (length(category) != 1)
{return(as.formula(paste("~I((", paste(category, collapse = " + "),")/A049)")))}
else{
 return(as.formula(paste("~I((", paste(coicop_to_lcf(category), collapse = " + "),")/A049)")))}
}

coicop_to_ghg_formula <- function(category) {
 # Append "GHG_" to access GHG emissions instead of expenditures
 if (length(category) != 1) {
  cats <- paste("GHG_", category,  sep="")
 }
 else{
 cats <- paste("GHG_", coicop_to_lcf(category),  sep="")
 }
 # Division by number of persons in HH (A049)
 return(as.formula(paste("~I((", paste(cats, collapse = " + "),")/A049)")))
}
```

Now lets compute total CO2 for all 12 COICOP categories
```{r}


CO2_full <- sapply(as.character(c(1:12)), function(x) MIcombine(with(svymi, svyby(coicop_to_ghg_formula(x), ~ReckwitzClass,svymean))))

CO2 <- CO2_full[1,] %>% simplify2array
CO2_SE <- sapply(CO2_full[2,], function(x) sqrt(diag(x)))

CO2 <- t(CO2)

CO2 <- rbind(CO2, colSums(CO2))
row.names(CO2)[13] <- "Total"


CO2
```


And plot it
```{r}
png(paste("coicop_co2_classes_relative","_", upper_threshold ,"up.png", sep=""))

image(round(t(CO2) / rowSums(t(CO2)) * 200)  ,xaxt="n",yaxt="n",ylab="COICOP categories", col=rocket(256, direction= -1))
#image(t(CO2/ rowSums(CO2)) ,xaxt="n",yaxt="n",ylab="COICOP categories", col=rocket(256, direction= -1))
axis(side=1, at=c(0,0.33,0.66,1.0), labels=levels(lcf$ReckwitzClass))
axis(side=2, at=seq(0,1, 1/12), labels=row.names(CO2), las=2)
grid(nx=4,ny=13,col="black")
dev.off()

```

# Utilities for formattable plotting


This can be used for nicer plots later on.
```{r}
#' altbind(df1, SE_df1)
#'
#' Bind together two dataframes in alternating column order
#' Assumes the first on contains mean values, and the second standard errors
altbind <- function(df1,df2) {
  assertthat::assert_that(ncol(df1) == ncol(df2))
  assertthat::are_equal(rownames(df1),rownames(df2))
  df3 <- data.frame(df1[,1], df2[,1])
  cns <- c(colnames(df1)[1], "SE")
  for (i in 2:ncol(df1)) {
    df3 <- data.frame(df3, df1[,i], df2[,i])
    cns <- c(cns, colnames(df1)[i], paste("SE", paste(rep(" ",i-1), collapse = ""), sep=""))
    }
  colnames(df3) <- cns
  rownames(df3) <- rownames(df1)
  return(df3)
}
```



```{r echo = FALSE}
my_proportion <- function(x) {
  x / max(S) # this is bad, it's using a global variable AAAAAHHHH
}
my_color_bar <- function (color = "lightgray", fixedWidth=200, probfunc=my_proportion,...) 
{
        formatter("span", style = function(x) style(display = "inline-block",
        direction = "rtl", `border-radius` = "4px", 
        `padding-right` = "2px", 
        `background-color` = csscolor(color), 
        width = paste(fixedWidth*probfunc(x),"px",sep=""),
        ...))
}
```

Saving needs this function and packages

```{r}
#library(htmltools)
#library(webshot2)

export_formattable <- function(f, file, width = "100%", height = NULL, 
                               background = "white", delay = 0.2, zoom = 2)
{
  w <- as.htmlwidget(f, width = width, height = height)
  path <- html_print(w, background = background, viewer = NULL)
  url <- paste0("file:///", gsub("\\\\", "/", normalizePath(path)))
  webshot(url,
          file = file,
          selector = ".formattable_widget",
          zoom = zoom,
          delay = delay,
          vheight = 900)
}
```

```{r}
smallfont <- formatter("span", style = x ~ ifelse(TRUE, "font-size:10px", NA))

```

# T-Test utitiles

```{r}
# from the lodown package

MIsvyttest<-function(formula, design , ...){

	# the MIcombine function runs differently than a normal svyglm() call
	m <- eval(bquote(mitools::MIcombine( with( design , survey::svyglm(formula,family=gaussian()))) ) )

	rval<-list(statistic=coef(m)[2]/survey::SE(m)[2],
			   parameter=m$df[2],
			   estimate=coef(m)[2],
			   null.value=0,
			   alternative="two.sided",
			   method="Design-based t-test",
			   data.name=deparse(formula))

	rval$p.value <- ( 1 - pf( ( rval$statistic )^2 , 1 , m$df[2] ) )

	names(rval$statistic)<-"t"
	names(rval$parameter)<-"df"
	names(rval$estimate)<-"difference in mean"
	names(rval$null.value)<-"difference in mean"
	class(rval)<-"htest"

	return(rval)

}

MIsvyttest(I(HighEdHH==1)~ReckwitzClass, subset(svymi, ReckwitzClass == "new middle" | ReckwitzClass == "old middle"))
```
For the t-test formulae

```{r}
coicop_to_ttest_formula <- function(category) {
 # Append "GHG_" to access GHG emissions instead of expenditures
 if (length(category) != 1) {
  cats <- paste("GHG_", category,  sep="")
 }
 else{
 cats <- paste("GHG_", coicop_to_lcf(category),  sep="")
 }
 # Division by number of persons in HH (A049)
 return(as.formula(paste("I((", paste(cats, collapse = " + "),")/A049)~ReckwitzClass")))
}
```


# Summary Statistics

```{r}

summary_forms <- sapply(c("~I(HighEdHH==1)", "~EqIncDOp", "~I(Ten1<=2)", "~I(Gorx == 7)"), as.formula) 

H_full <- sapply(summary_forms, function(x) MIcombine(with(svymi, svyby(x, ~ReckwitzClass,svymean))))


H_cts <- H_full[1,c(2)] %>% simplify2array %>% as.data.frame 
H_cts[,1] <- H_cts[,1] * 52
H_cts <- H_cts %>% round(digits=2)
H_cts[,1] <- H_cts[,1] %>% round
colnames(H_cts) <- c("Equivalised Income")

H_fct <- (H_full[1,c(1,3,4)] %>% simplify2array %>% as.data.frame)[5:8,]
H_fct <- (H_fct * 100)  %>% round(digits=2)
colnames(H_fct) <- c("% academic degree", "% owning house", "% in London")
rownames(H_fct) <- rownames(H_cts)

H_cts_SE <- sapply(H_full[2,c(2)], function(x) sqrt(diag(x))) %>% as.data.frame
H_cts_SE[,1] <- H_cts_SE[,1] * 52
H_cts_SE <- H_cts_SE %>% round(digits=2)
H_cts_SE[,1] <- H_cts_SE[,1] %>% round
colnames(H_cts_SE) <- colnames(H_cts)
H_cts_SE <- data.frame(apply(H_cts_SE, c(1,2),function(x) paste("±", x, sep="")))

H_fct_SE <- (sapply(H_full[2,c(1,3,4)], function(x) sqrt(diag(x))) %>% as.data.frame)[5:8,]
H_fct_SE <- (H_fct_SE * 100) %>% round(digits=2)
colnames(H_fct_SE) <- colnames(H_fct)
rownames(H_fct_SE) <- rownames(H_cts_SE)
H_fct_SE <- data.frame(apply(H_fct_SE, c(1,2),function(x) paste("±", x, sep="")))
 
S_form <- altbind(data.frame( H_fct %>% select(1), 
                              H_cts %>% select(1),
                              H_fct %>% select(2),
                              H_fct %>% select(3), check.names = FALSE),
                  data.frame( H_fct_SE %>% select(1), 
                              H_cts_SE %>% select(1),
                              H_fct_SE %>% select(2),
                              H_fct_SE %>% select(3),check.names = FALSE))


FT <- formattable(S_form, list(
  "% academic degree" = my_color_bar("violet",100, function(x) {x/100}),
  "SE" = smallfont,
  "Equivalised Income"= my_color_bar("tomato",100, proportion),
  "SE " = smallfont,
  "% owning house" = my_color_bar("orange",100, function(x) {x/100}), 
  "SE  " = smallfont,
  "% in London"= my_color_bar("lightskyblue",100, function(x) {x/100}),
  "SE   " = smallfont))               

FT               
```

```{r}
export_formattable(FT,paste("summary.png", sep=""), zoom = 2)

```

## HighEdHH in NMC not due to student households
```{r}
MIcombine(with(svymi, svyby(~I(HighEdHH==1), ~ReckwitzClass,svymean)))

```

# Totals

```{r}
glm_formula <- lcf %>% colnames %>% grep("GHG_", . , value=TRUE) %>% paste(collapse = " + ") %>% paste("I((", . , ")/A049) ~ EqIncDOp + I(HighEdHH==1)", sep = "") %>% formula

lin <- with(svymi, svyglm(glm_formula))

# for (mod in lin) {show(summ(mod))}

```




```{r}
# Households
#pop_per_class <- MIcombine(with(svymi, svytotal(~ReckwitzClass)))
# Persons
pop_per_class <- MIcombine(with(svymi, svyby(~A049, ~ReckwitzClass, svytotal)))
H <- pop_per_class$coefficients %>% round
H_SE <- pop_per_class$variance %>% diag %>% sqrt
```


```{r}
total_co2_formula <- lcf %>% colnames %>% grep("GHG_", . , value=TRUE) %>% paste(collapse = " + ") %>% paste("~I(", . , ")", sep = "") %>% as.formula
co2_per_class <- MIcombine(with(svymi, svyby(total_co2_formula, ~ReckwitzClass, svytotal)))
S <- (co2_per_class$coefficients * 52 / 1e6) %>% round
S_SE <- ((co2_per_class$variance %>% diag %>% sqrt) * 52 / 1e6) %>% round
```


```{r}
png(paste("totals_per_class","_", upper_threshold ,"up.png", sep=""))

# Create data

dat <- cbind(H, S)
colnames(dat) <- c("Population", "CO2")
rownames(dat) <- c("lower", "old middle", "new middle", "upper")
 
# create color palette:
library(RColorBrewer)
coul <- brewer.pal(4, "Set2") 
 
# Transform this data in %
data_percentage <- apply(dat, 2, function(x){x*100/sum(x)})

# Enable plotting outside
par(mar=c(5.2, 4.2, 4.2, 8.2), xpd=TRUE)
 
# Make a stacked barplot--> it will be in %!
bp <- barplot(data_percentage, col=coul, border="white", ylab="% of total")
legend("topright", legend=rev(rownames(dat)), fill=rev(coul), inset = c(-0.35,0), box.col="white")


y_pop <- c(data_percentage[1,1]/2, sum(data_percentage[1:2,1]) - data_percentage[2,1]/2,
           sum(data_percentage[1:3,1]) - data_percentage[3,1]/2, sum(data_percentage[,1]))

y_pop <- c(data_percentage[1,1]-5, sum(data_percentage[1:2,1]) - 5,
           sum(data_percentage[1:3,1])- 5, sum(data_percentage[,1])+1)
y_co2 <- c(data_percentage[1,2]-3, sum(data_percentage[1:2,2]) - 5,
           sum(data_percentage[1:3,2])- 5, sum(data_percentage[,2]))



xpos <- c(.7,.7,.7,.7,1.9,1.9,1.9,1.9)
ypos <- c(y_pop, y_co2)
text(bp, x=xpos, y=ypos, labels=paste(as.vector(round(data_percentage, digits=1)),"%")
, pos=1)

dev.off()
```





# High Level View on CO2

```{r echo = FALSE}


highlevel_codes <- list(coicop_to_lcf("4"), coicop_to_lcf("7"),
  setdiff(B %>% select(LCFCODE) %>% unlist %>% as.character, c(coicop_to_lcf("4"), coicop_to_lcf("7"))), B %>% select(LCFCODE) %>% unlist %>% as.character)

H_full <- sapply(highlevel_codes, function(x) MIcombine(with(svymi, svyby(coicop_to_ghg_formula(x), ~ReckwitzClass,svymean))))

H <- H_full[1,] %>% simplify2array %>% as.data.frame 
H_SE <- sapply(H_full[2,], function(x) sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits=2)
colnames(S) <- c("Housing", "Transport", "Indirect Consumption", "Total")


S_SE <- (H_SE * 52 / 1000) %>% round(digits=2)
colnames(S_SE) <- c("Housing", "Transport", "Indirect Consumption", "Total")
S_SE <- apply(S_SE, c(1,2),function(x) paste("±", x, sep=""))


S_Form <- altbind(S, S_SE)
```


```{r echo = FALSE}

FT <- formattable(S_Form,
            align=c("r","l","r","l","r","l"),
            list("Housing" = my_color_bar("orange"),
                 "SE" = smallfont,
                 "Transport" = my_color_bar("lightskyblue"),
                 "SE " = smallfont,
                 "Indirect Consumption" = my_color_bar("violet"),
                 "SE  " = smallfont,
                 "Total" = my_color_bar("tomato"),
                 "SE   " = smallfont))
FT
```



```{r}
export_formattable(FT,paste("highlevel","_", upper_threshold ,"up.png", sep=""), zoom = 2)
```


T-testing of middle class differences

```{r}
T_full <- sapply(highlevel_codes, function(x) MIsvyttest(coicop_to_ttest_formula(x), subset(svymi, ReckwitzClass == "new middle" | ReckwitzClass == "old middle")))
T_full
```




# Zoom in...
##... on Housing

```{r}
housing_codes <- list(coicop_to_lcf("4.4.1"), coicop_to_lcf("4.4.2"),
  setdiff(coicop_to_lcf("4"), c(coicop_to_lcf("4.4.1"), coicop_to_lcf("4.4.2"))),
  coicop_to_lcf("4"))
  


H_full <- sapply(housing_codes, function(x) MIcombine(with(svymi, svyby(coicop_to_ghg_formula(x), ~ReckwitzClass,svymean))))


H <- H_full[1,] %>% simplify2array %>% as.data.frame 
H_SE <- sapply(H_full[2,], function(x) sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits=2)
colnames(S) <- c("Electricity", "Gas", "Other", "Total")


S_SE <- (H_SE * 52 / 1000) %>% round(digits=2)
colnames(S_SE) <- c("Electricity", "Gas", "Other", "Total")
S_SE <- apply(S_SE, c(1,2),function(x) paste("±", x, sep=""))


S_Form <- altbind(data.frame(S), data.frame(S_SE))

FT <- formattable(S_Form,
            align=c("r","l","r","l","r","l","r","l"),
            list("Electricity" = my_color_bar("orange",100),
                 "SE" = smallfont,
                 "Gas" = my_color_bar("lightskyblue",100),
                 "SE " = smallfont,
                 "Other" = my_color_bar("violet",100),
                 "SE  " = smallfont,
                 "Total" = my_color_bar("tomato",100),
                 "SE   " = smallfont))

FT

```

```{r}
export_formattable(FT,paste("housing.png", sep=""), zoom = 2)
```

T-testing of middle class differences

```{r}
T_full <- sapply(housing_codes, function(x) MIsvyttest(coicop_to_ttest_formula(x), subset(svymi, ReckwitzClass == "new middle" | ReckwitzClass == "old middle")))
T_full
```

## ... on Mobility



```{r}
# car_codes: "7.1." - "7.1.3.3" + "7.2." - "7.2.1.4" + "7.3.4.7" (car leasing)
# other: "7.1.3.3" + "7.2.1.4" (bicycles) + "7.3.4.4" + "7.3.4.5" (taxis and other) + "7.3.4.6" (car, van, bicycle hire)
# public transport: 7.3.1, 7.3.2, 7.3.3, 7.3.4.3(school), 7.3.4.8(water)
# air transport: 7.3.4.1, 7.3.4.2

car_codes <- setdiff(sapply(c("7.1", "7.2", "7.3.4.7"), coicop_to_lcf) %>% unlist,
                     sapply(c("7.1.3.3", "7.2.1.4"), coicop_to_lcf) %>% unlist)
pubtrans_codes <- sapply(c("7.3.1", "7.3.2", "7.3.3","7.3.4.3", "7.3.4.8"), coicop_to_lcf) %>% unlist %>% as.character

air_codes <- sapply(c("7.3.4.1", "7.3.4.2"), coicop_to_lcf) %>% unlist %>% as.character

mobility_codes <- list(car_codes, pubtrans_codes, air_codes, coicop_to_lcf(7))
  

H_full <- sapply(mobility_codes, function(x) MIcombine(with(svymi, svyby(coicop_to_ghg_formula(x), ~ReckwitzClass,svymean))))


H <- H_full[1,] %>% simplify2array %>% as.data.frame 
H_SE <- sapply(H_full[2,], function(x) sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits=2)
colnames(S) <- c("Cars", "Public", "Air", "Total")


S_SE <- (H_SE * 52 / 1000) %>% round(digits=2)
colnames(S_SE) <- c("Cars", "Public", "Air", "Total")
S_SE <- apply(S_SE, c(1,2),function(x) paste("±", x, sep=""))



internet_full <- MIcombine(with(svymi, svyby(coicop_to_ghg_formula("8.4"), ~ReckwitzClass,svymean)))
Internet <- (internet_full$coefficients * 52 / 1000) %>% round(digits=3)
internet_SE <- internet_full$variance  %>% diag %>% sqrt 
internet_SE <- (internet_SE *  52 / 1000) %>% round(digits=4)
internet_SE <- sapply(internet_SE,function(x) paste("±", x, sep=""))

S_Form <- altbind(data.frame(S, Internet, check.names = FALSE), data.frame(S_SE, internet_SE))


FT <-formattable(S_Form,
            align=c("r","l","r","l","r","l","r","l"),
            list("Cars" = my_color_bar("orange",100),
                 "SE" = smallfont,
                 "Public" = my_color_bar("lightskyblue",100),
                 "SE " = smallfont,
                 "Air" = my_color_bar("violet",100),
                 "SE  " = smallfont,
                 "Total" = my_color_bar("tomato",100),
                 "SE   " = smallfont,
                 "Internet" = my_color_bar("pink",50, proportion),
                 "SE    " = smallfont))

FT
```

```{r}
export_formattable(FT,paste("mobility","_", upper_threshold ,"up.png", sep=""), zoom = 2)

```

T-testing of middle class differences

```{r}
T_full <- sapply(mobility_codes, function(x) MIsvyttest(coicop_to_ttest_formula(x), subset(svymi, ReckwitzClass == "new middle" | ReckwitzClass == "old middle")))
T_full
```

## ... on Indirect Consumption



```{r}

all_consumption_codes <- setdiff(B %>% select(LCFCODE) %>% unlist %>% as.character, c(coicop_to_lcf("4"), coicop_to_lcf("7")))


meat_codes <- sapply(c("1.1.5","1.1.6", "1.1.7","1.1.8","1.1.9","1.1.10"), coicop_to_lcf) %>% unlist %>% as.character

other_food_codes <- setdiff(coicop_to_lcf(1), meat_codes)

other_consumption_codes <- setdiff(all_consumption_codes, c(meat_codes, other_food_codes, coicop_to_lcf(11))) # COICOP 11 -> Restaurants, Holidays
  
consumption_codes <- list(meat_codes, other_food_codes, coicop_to_lcf(11),other_consumption_codes,  all_consumption_codes) # 
  

H_full <- sapply(consumption_codes, function(x) MIcombine(with(svymi, svyby(coicop_to_ghg_formula(x), ~ReckwitzClass,svymean))))


H <- H_full[1,] %>% simplify2array %>% as.data.frame 
H_SE <- sapply(H_full[2,], function(x) sqrt(diag(x))) %>% as.data.frame


S <- (H * 52 / 1000) %>% round(digits=2)
colnames(S) <- c("Meat*", "Other Food*",  "Restaurants, Holidays*", "Other Indirect Consumption","Total")# "Other Consumption"


S_SE <- (H_SE * 52 / 1000) %>% round(digits=2)
colnames(S_SE) <- colnames(S)
S_SE <- apply(S_SE, c(1,2),function(x) paste("±", x, sep=""))



S_Form <- altbind(S, S_SE)


FT <- formattable(S_Form,
            align=c("r","l","r","l","r","l","r","l"),
            list("Meat*" = my_color_bar("orange",200),
                 "SE" = smallfont,
                 "Other Food*" = my_color_bar("lightskyblue",200),
                 "SE " = smallfont,
                 "Restaurants, Holidays*" = my_color_bar("violet",200),
                 "SE  " = smallfont,
                 "Other Indirect Consumption" = my_color_bar("pink",100),
                 "SE   " = smallfont,
                 "Total" = my_color_bar("tomato",100),
                 "SE    " = smallfont))

FT
```

```{r}
export_formattable(FT,paste("consumption","_", upper_threshold ,"up.png", sep=""), zoom = 2)
```

T-testing of middle class differences

```{r}
T_full <- sapply(consumption_codes, function(x) MIsvyttest(coicop_to_ttest_formula(x), subset(svymi, ReckwitzClass == "new middle" | ReckwitzClass == "old middle")))
T_full
```
