---
title: "Preprocessing: Imputation of missing education values"
author: "Michael Lindner"
date: "6/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = ".")
```

# Preliminaries: Version control

For exact reproducibility of our results we use the package manager `renv` to keep track of the versions of all packages used.

To reproduce our analysis, install `renv` then use `renv::activate()` to activate the environment specified in the lockfile. You might have to use `renv::hydrate()` to install required packages as well. Afterwards you can run the R code as you would normally do.

Troubleshooting: `renv::restore()`



# Load librariers and data set

We begin by loading libraries...

```{r message=FALSE}
library("haven")
library("dplyr")
library(tidyr)
library(labelled)
library(mice)
```
This time we need data from several of the lcf data sets
```{r}
lcf <- read_sav("../data/lcf.sav")
rawper <- read_sav("../data/raw/2018_rawper_ukanon_final.sav")
weekly_ghg_hh <- read_sav("../data/weekly_ghg_hh.sav")
```
Join GHG to expenditure data

```{r}
lcf <- full_join(lcf, weekly_ghg_hh, by="case")
```

Set random seed for reproducibility
```{r}
set.seed(123)
```


## Highest education per household


```{r}
# Check number of NAs in individual dataset (40.1% missing)
sum(is.na(rawper$HighEd1))


# Introduce a new factor level for people that are in Education (School) 
rawper$HighEd1[!is.na(rawper$School)] <- 9
# Introduce a new factor level for people that are in Education (University) 
rawper$HighEd1[rawper$TypeEd == 5] <- 10

# Check number of NAs again
is.na(rawper$HighEd1) %>% sum
```

```{r}
rawall <- full_join(rawper, lcf, by = "case")
```



## MICE

Summarize ethnicity variable
```{r}
rawall$Ethp <- rawall$EthEp
rawall$Ethp[!is.na(rawall$EthNIp)] <- rawall$EthNIp[!is.na(rawall$EthNIp)]
rawall$Ethp[!is.na(rawall$EthSp)] <- rawall$EthSp[!is.na(rawall$EthSp)]
rawall$Ethp[!is.na(rawall$EthWp)] <- rawall$EthWp[!is.na(rawall$EthWp)] 
```


We arrive at the predictors for predictive mean matching (PMM) via the following strategy:
* Select from literature (income, sex, ethnicity, geography)
```{r}
pred_literature <- c("Ten1",
                     "Sex",
                     "Gorx",
                     "A094", # socio economic status of HRP
                     "EcStatus", # socio economic status
                     "Ethp", # ethnicity 
                     "EqIncDOp", # household inc
                     "GWkIncp", # personal income
                     "a111p", # rooms
                     "G018", # adults
                     #"G019", # children
                     "a070p" # age of oldest person in HH
                     #"a065p", # age of HRP
                     #"DVAge18" # age of person
                     ) 
```

* Test the quality of the linear model and remove insignificant predictors
```{r}
dfimp <- rawall %>% select(case,HighEd1,pred_literature)
dfimp[,2:8] <- lapply(dfimp[,2:8] %>% zap_labels, as_factor)
dfimp[,9:ncol(dfimp)] <- dfimp[,9:ncol(dfimp)] %>% zap_labels


# Test the quality of the linear model
L <- glm(HighEd1 ~ ., dfimp[,2:ncol(dfimp)], family = binomial())
summary(L)
#library(jtools)
#summ(L)
```
We impute the missing values with predictive mean matching and study the plausibility and convergence of the generated imputations.

```{r}

imp <- mice(dfimp,  m = 6, method = "pmm", print=FALSE, maxit=10)
densityplot(imp, ~HighEd1)
plot(imp)
```
Join with lcf data
```{r}
iml <- complete(imp, "all", include=TRUE)

mil <- lapply(iml, function(x) x %>% select(case, HighEd1) %>%  group_by(case) %>%
  slice_min(order_by = HighEd1, with_ties=FALSE) %>%
  rename(HighEdHH = HighEd1) %>% full_join(lcf, by = "case"))

```

And save

```{r}
saveRDS(mil, file="../data/lcf_milper.rds")
```


